\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyvrb}
\usepackage{listings}
\usepackage{color}
\usepackage{textcomp}
\DefineShortVerb{\|}

\hypersetup{
    colorlinks=true,      
    urlcolor=red      
}

\lstset{
  tabsize=2,
  rulecolor=,
  language=haskell,
  basicstyle=\normalsize,
  upquote=true,
  aboveskip={1.5\baselineskip},
  columns=fixed,
  showstringspaces=false,
  extendedchars=true,
  breaklines=true,
  prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{}},
  showtabs=false,
  showspaces=false,
  showstringspaces=false,
  identifierstyle=\ttfamily,
  keywordstyle=\color[rgb]{0,0,1},
  commentstyle=\color[rgb]{0.133,0.545,0.133},
  stringstyle=\color[rgb]{0.627,0.126,0.941},
}

\title{Sytyc-1.0}
\author{Xavier Ho,\quad s2674674}
\date{\today}

\begin{document}
\maketitle

\section*{\centering \small Abstract}

\href{https://github.com/SpaXe/Sytyc}{Sytyc} is a web-based programming puzzles database with a compiler on the server side.  The web interface automatically parses the system sub-folders and generates a list of problems end-users can pick from.  The end-user solves the problem and submits some source code.  Then, Sytyc compiles and runs the code on the server, and checks if the program passes all tests.  Errors are reported directly on the webpage.  Successful programs will past all tests, and the end-user is congratulated.

\section{Background}

Originally started as "Judge", Sytyc was conceptualised to provide students an independent platform where they can test their programs, while solving puzzles with difficulties ranging from introductory to very difficult.  It also serves as a platform to train ICPC programming competition participants: format of the puzzles has been bulit similar to the competition format.  Sytyc archives puzzles by the subfolders in the file system, which is easy to backup and maintain.

There are existing websites that have done an excellent job, such as \href{http://www.topcoder.com/}{TopCoder} and \href{http://projecteuler.net/}{ProjectEuler}.  Sytyc is an attempt to recreate some features from these sites in order to customise the types of problems in the database, appropariate for the target programmers at Griffith University.  In addition, Sytyc supports Andrew Rock's \href{http://www.ict.griffith.edu.au/arock/MaSH/index.html}{MaSH} compiler, which is consistent with the offering with the introductory programming course on Nathan campus.

\section{Installation}

This installation guide assumes the reader is familiar with basic Unix commands and its operating system envorinment.

\subsection{Checking out the source code}

If, for some reason, the source code was not provided along with the manual, you can always obtain the latest version of Sytyc at its  \href{https://github.com/SpaXe/Sytyc}{Github repository}.

If you're not a Git user, download and install \href{http://git-scm.com/}{Git}.  Open up a terminal and check out the soure code with:
\begin{verbatim}
git clone git@github.com:SpaXe/Sytyc.git
\end{verbatim}

\subsection{Compiling the source code}

Sytyc requires the following dependencies to be installed:
\begin{verbatim}
GHC 7.0.3       pandoc-1.8      missingH-1.1.0.3
\end{verbatim}
in addition to the \href{http://hackage.haskell.org/platform/}{Haskell Platform} (2011.2.0.1).  Sytyc has been tested on Windows 7 64-bit with XAMPP 1.7.4, compiled against the Haskell Platform of the version above.  A compile-only test was run on Ubuntu 11.04 32-bit.  The server must support CGI for Sytyc to function.  

Move the Sytyc source code to a CGI-enabled folder.  The index page in your server settings should be index.cgi.

If you're on Windows, in the main folder of Sytyc simply type
\begin{verbatim}
make
\end{verbatim}

If you're on Mac OS X or Linux, in the main folder of Sytyc type
\begin{verbatim}
cd src
make
make install
cd ..
\end{verbatim}

You should see several |.cgi| files being compiled and moved to the main folder.  Open up a web browser and check that you can see the main webpage.  Ensure your CGI environment permission is set properly so that connections cannot see your subdirectories for basic security.

\section{Using Sytyc}
The majority of Sytyc should be self-explanatory as you explore the webpage.  This version of Sytyc supports only MaSH source code with the \href{http://www.ict.griffith.edu.au/arock/MaSH/console.html}{console} environment.  You are encouraged to try the sample problems and see Sytyc in action.

If you encounter any issues, please contact Xavier at \href{mailto:contact@xavierho.com}{contact@xavierho.com}.

\section{Customising Sytyc}
Thanks to the \href{http://daringfireball.net/projects/markdown/}{Markdown} syntax, the majority of the webpage is generated by plaintext templates found in the |templates| folder.  There are two types of templates: HTML files, and |.md| files.

\subsection{HTML Files}

|template.html| contains the main structure of the entire webpage, from the |DOCTYPE| all the way to the end. You will see certain template variables surrounded by the |$| sign.  These variables are substituted with the appropriate content at run-time.

|problems.html| (plural) is a partial webpage that contains the HTML structure for a list of problems.

|problem.html| (singular) is also a partial webpage that contains the HTML structure for displaying a problem description, an example of input and output, as well as the textarea in which end-users can submit their source code.

\subsection{Markdown Files}

\href{http://daringfireball.net/projects/markdown/syntax}{Here is the complete reference of the markdown syntax}.  Generally speaking, the markdown files are very easy to understand and modify.  An example looks like:
\begin{verbatim}
Sytyc - Programming Puzzles
===========================
If you're here, you probably can program in at least one language.
Perhaps you wanted to learn a new language, or perhaps you just
wanted to tackle some programming challenges.

Whatever the reason is, welcome.

Get Started
-----------
If you're a first-timer,
[check out the list of problems here](problem_list.cgi). Get your 
compiler or interpreter and your favourite IDE ready, and start
coding.  All problems use the standard output for printing, and
standard input for reading.

Got questions?
--------------
There is a list of [Frequently Asked Questions](faq.cgi). If your
question isn't on the list, you can [give us a shout](feedback.cgi).

What is Sytyc?
--------------
Sytyc is an interface where you can view programming puzzles, and
submit your answers in source code.  It's entirely written in
Haskell, and runs via CGI on any web browser.  It's also a great
place to learn programming.
\end{verbatim}

Note that hyperlinks is simply |[display-name](link)|. '|=|' denotes a |h1| in HTML-speak, while a '|-|' denotes a h2.  You don't have to recompile Sytyc if you modify these |.md| templates---they are parsed at run-time.

\subsection{Adding and Changing Puzzles}

Upon inspection of the |problems| folder, you will find a list of problems.  In each one, you will find:
\begin{verbatim}
description.md  input   output  Generator.mash  Solution.mash
\end{verbatim}

Both |input| and |output| contains files such as these:
\begin{verbatim}
01.txt  02.txt
\end{verbatim}

|description.md| is the markdown template for a puzzle's description, constraints, as well as sample input and output.  An example:
\begin{verbatim}
Summation
=========
Write a program that reads a list of integers, and prints the
sum of all numbers read.

Example Input
-------------
    1
    4
    6
    6
    3

Example Output
--------------
    20
    
Constraints
-----------
*   Up to 1,000 integers could be supplied at once.

*   Each integer will range between 0 and 1,000, inclusive.

*   Your program must take no longer than 1 minute to execute.
\end{verbatim}

Note that lists are denoted by `|*|` followed by some whitespaces.  Similar to other markdown files, no re-compile is needed if this file is changed.  In addition, you can copy and paste the puzzles folder (i.e. |0001_Summation|) in the same folder, rename it, and Sytyc will pick it up as a new problem and list it on the webpage---all without the need to re-compile.  The problems are listed in lexical order.

Sample input and output are indented by 4 spaces. This puts them inside |<code>| in the result HTML for styling.

The |input| and |output| folders contain files that will be used to test a submitted program.  For example, |input/01.txt| is used to input to the program, with its output compared to |output/01.txt|, and so on.  They don't have particular naming constraints---Sytyc will parse through them all---but the names must be consistent between both folders.

|Generator.mash| and |Solution.mash| are unused by Sytyc, but internally they were created to generate the input and output files.  This is currently a manual process.

Test that you can add a new puzzle by duplicating a puzzle folder, rename it, and change its descrption as well as input and output.  Remember re-compile is not necessary to change the puzzles.
\pagebreak
\section{Sytyc.hs}
Located in |src/Sytyc.hs|, it contains the common file-parsing functions as well as handling presentation logic.  All other source import the module |Sytyc|.

\subsection{Constants}
\begin{tabular}{ p{1.5in}p{3in} }
|prog_name| & Title of the webpage, as well as the name displayed on the homepage. \\
|version| & Sytyc software version. \\
|problem_dir| & Directory where the puzzles are located. \\
|template_dir| & Directory where the HTML and markdown templates are located. \\
|tmp_dir| & Directory where temporary source code is stored for compilation at run-time. \\
|supported_languages| & Supported languages that run on Sytyc;  Currently, only MaSH is. \\
|problem_file| & File name for the puzzle description template. \\
|result_file| & File name for the puzzle submission result template. \\
|template_html| & File path for |template.html|. \\
|problems_html| & File path for |problems.html|. \\
|problem_html| & File path for |problem.html|.
\end{tabular}

\subsection{Methods}
The following is a list of methods found in Sytyc module. \\

|parseTemplate :: [(String, String)] -> String -> IO String|
\vskip 0.1in
Synonym for Pandoc's renderTemplate.  Takes a list of string (|key|, |value|) pairs, and a string to be parsed. For every match of the |key| (wrapped in |$| sign in the template), it will be replaced by the |value|.  Returns the newly replaced string.\\

|exReadFile :: FilePath -> IO String|
\vskip 0.1in
Takes a |path| of a file, reads it, and returns the content of the file with error handling.\\

|parseTemplateFile :: [(String, String)] -> FilePath -> IO String|
\vskip 0.1in
Equivalent to |parseTemplate|, except the second argument is a |path| to a file that will be opened for reading using |exReadFile|.\\

|parseMarkdownFile :: FilePath -> IO String|
\vskip 0.1in
Takes a |path| to a markdown (|.md|) file, and returns its HTML translation.\\\pagebreak

|parseResultTemplate :: String -> IO String|
\vskip 0.1in
Takes the string and inserts it into the result template.  Returns the result in HTML.\\

|nToBR :: String -> String|
\vskip 0.1in
Replaces the |\n| in the input string with |<br>|.\\

|getProblemList :: IO [String]|
\vskip 0.1in
Returns a list of problem names.\\

|build_time :: IO String|
\vskip 0.1in
Returns the current system time.\\

|footer_text :: IO String|
\vskip 0.1in
Returns the footer text in the webpage.

\section{Specific Methods}

|problem.hs| contains the routines that call the compilers, and provides a simple CGI to interface with the web browser.

\subsection{Methods}

The following is a list of methods used in Sytyc.\\

|runJava :: String -> String -> IO (String, ExitCode)|
\vskip 0.1in
Takes some Java |source| code and a string to be redirected into standard |input|.  Returns a tuple of the |output| and the exit |code|.\\

|runMash :: String -> String -> IO (String, ExitCode)|
\vskip 0.1in
Takes some MaSH |source|code and a string to be redirected into standard input.   Returns a tuple of the |output| and the exit |code|.\\

|verifyProgram :: String -> String -> [FilePath] -> [FilePath]|\\
|                 -> IO String|
\vskip 0.1in
Takes some |source| code, |langauge| of the program, a list of |inputs| and |outputs|.  Returns a message to the user saying if their program was successful or not. \\

|getProblemIO :: String -> IO ([FilePath], [FilePath])|
\vskip 0.1in
Takes the |name| of the problem, and returns a tuple of lists of its |inputs| and |outputs|.\\\pagebreak

\subsection{Common Methods}

|cgiMain :: CGI CGIResult|
\vskip 0.1in
Handles the front controller logic.  This method's implmentation is different from file to file.

\subsection{Unused Methods}

|runghc :: String -> String -> IO (String, ExitCode)|
\vskip 0.1in
{\em Warning: Untested at integration stage.}

Takes some Haskell |source|code and a string to be redirected into standard input.   Returns a tuple of the |output| and the exit |code|.

\section{Limitations and Issues}

Sytyc works on the basis which the program must be: 1) written in MaSH; 2) uses the |console| environment; 3) runs in finite time.  While it does have Java and Haskell support, they are not available to end-users for security reasons.  This security issue is a solved problem but not implemented in Sytyc.  In addition, the current |runMash| function does not impose a timeout limit on the program; the result of an never-ending program is undefined.

Currently, there is no mechanism to automate puzzle generations. All puzzles must be manually created, written, and supplied.  The input and output files are also static files; no random number generation is currently set to test if the input solution is robust.  Partially this was due to the fact that File I/O is very expensive, and generating multiple files per user did not seem feasible.  A possible solution might be to provide an input test directly in the source, but this was unexplored.

Haskell's static linking cause the compiled binary to be above 10MB.  As a web-service this seems unacceptable, especially when one considers the fact that exactly the same libraries are linked and copied to each |.cgi| file.  However this will not cause the website to slow down since the executable is only run on the server, and only the result string is sent to the client.  Nonetheless, the size of the binaries is too big and a problem native to Haskell.

In terms of software design, I felt the program could have been written with more structure, e.g, using Haskell's typeclass system more, and create a flexible program.  The current stage is a working prototype.  While it does provide the benefit of no-need-to-recompile when one wishes to add or modify its contents, its extensibility is rather limited by design.

\section{Course-related comments}
I learned a lot about Haskell, and this is wonderful news.  However, I also felt that the assignments were unfortunately restricted to the course environment, and not much Haskell design was explored as a main goal.  In particular, the assignments felt they should have been for a project-based course (similar to the Third Year Project, or an Advanced Studies project) rather than a research-based course.  The workload per assignment, in my own estimates, was at least 60 hours each, which is longer than desired.

Instead, I would suggest that the assignments should be more focused on langauge practice and function design.  The practice sheets that were given in the first half of the course were very useful.  I would like to see more of them---they got me thinking harder than the assignments, which felt like a big hack in the end.  

Aside from that, it was defintiely a very solid course, and I thoroughly enjoyed it.  I would recommend anyone interested in functional languages to take it.

\section{Contact information}

You can reach Xavier at \href{mailto:contact@xavierho.com}{contact@xavierho.com}.

\end{document}























